---
title: "Course Project PML"
output: html_document
---

This is the Course Project from Practical Machine Learning Course, in which the data about personal activity from <http://groupware.les.inf.puc-rio.br/har> should be classified a variable "classe".


### Library

The primary machine learning library which was used was "caret".
```{r, eval = FALSE}

library(caret);

```


### Download Data

This function downloading the csv data if required.
```{r, eval = FALSE}

downloadData <- function() {
  if (!file.exists("pml-data")) {
    dir.create("pml-data");
  }
  
  download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", 
                "./pml-data/pml-training.csv");
  download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", 
                "./pml-data/pml-testing.csv");
} 

```


### Cleanup Data

This function count all NA-Values per column, remove all columns with NA-Values and remove the first seven columns with identity content.
```{r, eval = FALSE}

cleanupData <- function(dataTrain) {
  
  naValues  <- apply(dataTrain, 2, function(x) {sum(is.na(x))});
  dataTrain <- dataTrain[,which(naValues == 0)];
  
  dataTrain <- dataTrain[,8:length(dataTrain)];
  
  return (dataTrain);
}

```


### Train Model

After load and cleanup the plm train data, split the data into train and crossvalidation set´s, and train a modelObj with the random forest algorithmen. 
```{r, eval = FALSE}

#downloadData();
plmTrain           <- read.csv("./pml-data/pml-training.csv", na.strings= c("NA",""," "));
plmTrain           <- cleanupData(plmTrain);

set.seed(3888);

indexTrain         <- createDataPartition(y = plmTrain$classe, p = 0.7, list = FALSE)
plmTrainTraining   <- plmTrain[indexTrain, ]
plmTrainCrossval   <- plmTrain[-indexTrain, ]


modelObj           <- train(classe ~., data=plmTrainTraining, method="rf");

```


### Validate Model

Predict the values for the crossvalidation set and plot the confusionMatrix. The out of sample error is 0,0054 and the accuracy 0,9946.
```{r, eval = FALSE}

predictCrossvalResult  <- predict(modelObj, plmTrainCrossval)
confusionMatrix(plmTrainCrossval$classe, predictCrossvalResult)

```


### Validate Model

Load, cleanup and predict the values for the plm test set.
```{r, eval = FALSE}

plmTest <- read.csv("./pml-data/pml-testing.csv", na.strings= c("NA",""," "))
plmTest <- cleanupData(plmTest);

predictTestResult <- predict(modelObj, plmTest)
predictTestResult

```


